---
title: "Lab11"
author: "Lingchen Lou"
date: "2018/11/25"
output: pdf_document
---
```{r}
library(tidyverse)
library(microbenchmark)
library(ggplot2)
```


#Question 1. 
Write a function that generates numbers from binomial(n, p) distribution using runif() function. 
Hint: binomial(n, p) random variable can be defined as a sum of n independent Bernoulli(p) random variables.
```{r}
set.seed(1)

binom <- function(l,n,p) {
  bin_data<-NULL
  for (i in 1:l){
    x<-runif(n, min=0, max=1)
    bin_data[i] = sum(as.numeric(x < p))
  }
  return(bin_data)
}

binom(1,100, 0.4)
rbinom(1,100,0.4)

```
# Question 2. 
Compare performance of your function with rbinom() using microbenchmark() function.
```{r}
microbenchmark(binom(1,100,0.4),rbinom(1,100,0.4))
```



# Question 3. 
Suppose we want to simulate data from a linear regression model: 
$Y_i = \beta_0 + \beta_1\times x_i+\epsilon_i$, $i=1, ...,N$, where $\epsilon$ ~ $N(0,3)$ and X is a covariate that ranges between 20 and 40. Let $\beta_0$ = 15 and $\beta_1$ = 0.4 are known coefficients. Generate data (N = 50) from this models with given coefficients. Fit a linear regression model and plot fitted values vs residuals using ggplot() function. Please do not forget to use set.seed() function for reproducibility.
```{r}
set.seed(999)

n <- 50
e<-rnorm(n,0,3)
x<-runif(50,min = 20,max=40)
y<-15+0.4*x+e

mod1 <- lm(y~x)
#scatter plot
plot(x,y)
abline(lm(y~x))
#plot fitted values vs residuals
ggplot() + 
  geom_point(aes(x=mod1$fitted.values, y=mod1$residuals))+
  labs(x = "fitted values", y = "residuals", title = "Plot for fitted values vs. residuals")


```



# Question 4 
Box-Muller algorithm: generate $U_1$ and $U_2$ two independent uniform(0, 1) random variables and set: $R = -2log(U_1)$ and $\theta = 2\pi U_2$ then $X = R$cos($\theta$) and $Y = R$sin($\theta$) are two independent normal variables. Write a function that generates normal variates using Box-Muller algorithm. Compare simulated data from your function with simulated data from rnorm() function using ggplot() (histogram?).
```{r}
set.seed(999)
box_muller <- function() {
  u1 <- runif(1)
  u2 <- runif(1)
  
  r <- sqrt(-2*log10(u1))
  theta <- 2*pi*u2
  
  x <- r * cos(theta)
  y <- r * sin(theta)
  return(c(x,y))
}

data_box<-replicate(1000,box_muller())
data_box<-data.frame(x=data_box[1,],y=data_box[2,])

ggplot()+geom_density(aes(x=rnorm(1000), fill = "normal"),alpha=0.5)+
  geom_density(aes(x=data_box$x, fill = "variable x"),alpha=0.5) +
  geom_density(aes(x=data_box$y, fill = "variable y"),alpha=0.5)

```
It seems like the variable X and Y produced in Box-Muller alogrithm are normal distributed.